---
title: "IntArch_ClayTools_Adult_Model"
author: "Ethan Hurwitz, Tim Brady, Adena Schachner"
date: "12/21/2018"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
library(tidyverse)
```

## Set Parameters
```{r set parameters}
# --- Parameters: these are example parameter values, for comprehension purposes ---
# --- Trial information:
# Box - which puzzle box (Star, Circle)
Box <- 'Star'
# HandleIsDiff - 0 = handles are identical; 1 = handles are different
HandleIsDiff <- 0
# RodIsDiff - 0 = rods are identical; 1 = rods are different
RodIsDiff <- 0
# NumRodChoices - 2 or 10 options to choose from
NumRodChoices <- 10
# NumHandleChoices - 2 or 10 options to choose from
NumHandleChoices <- 10
# Response (someone copied; or made independently, without copying)
Response <- "Someone copied."

# --- These will be set using MLE; here are sample values for comprehension purposes
# priorCopy - prior on copying
priorCopy <- .15
# errorRate - If you are trying to copy, how likely is it that you make a mistake and choose a different piece?
errorRate <- .03
# nChoices - for model that ignores number of options (for rod/handles pieces), how many options does it assume were available?
nChoices <- 10
```

#Model base - code that is common to all 4 alternative models
##Model base
```{r model base}
ModelBase = function(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate){
  
  # RodIsDiff and HandleIsDiff are logicals (0/1, or T/F)
  likelihoodIfCopyingHandleOnly <- ((RodIsDiff)     * ((NumRodChoices-1)/NumRodChoices) + # if rod is different
                                    (1-RodIsDiff)   * (1/NumRodChoices)) *             # if rod is the same
                                   ((HandleIsDiff)  * errorRate +                   # if handle is different
                                    (1-HandleIsDiff)* (1-errorRate))                # if handle is the same
  
  likelihoodIfCopyingRodOnly <-   ((RodIsDiff)      * errorRate +
                                   (1-RodIsDiff)    * (1-errorRate)) *
                                  ((HandleIsDiff)   * ((NumHandleChoices-1)/NumHandleChoices) + 
                                   (1-HandleIsDiff) * (1/NumHandleChoices))
  
  likelihoodIfCopyingAll <-       ((RodIsDiff)      * errorRate +
                                   (1-RodIsDiff)    * (1-errorRate)) *
                                  ((HandleIsDiff)   * errorRate +
                                   (1-HandleIsDiff) * (1-errorRate))
  
  likelihoodIfNoCopying <-        ((RodIsDiff)      * ((NumRodChoices-1)/NumRodChoices) +
                                   (1-RodIsDiff)    * (1/NumRodChoices)) *
                                  ((HandleIsDiff)   * ((NumHandleChoices-1)/NumHandleChoices) +
                                   (1-HandleIsDiff) * (1/NumHandleChoices))

  # priors here are specified as rod, then handle
  AdjustedLikelihoodIfCopyingAll        <- priorCopy     * priorCopy     * likelihoodIfCopyingAll
  AdjustedLikelihoodIfCopyingHandleOnly <- (1-priorCopy) * priorCopy     * likelihoodIfCopyingHandleOnly
  AdjustedLikelihoodIfCopyingRodOnly    <- priorCopy     * (1-priorCopy) * likelihoodIfCopyingRodOnly
  AdjustedLikelihoodIfNoCopying         <- (1-priorCopy) * (1-priorCopy) * likelihoodIfNoCopying
  
  SumAdjustedLikeCopy <- AdjustedLikelihoodIfCopyingAll + 
                           AdjustedLikelihoodIfCopyingHandleOnly + 
                           AdjustedLikelihoodIfCopyingRodOnly
  
  PosteriorCopying <- SumAdjustedLikeCopy / (AdjustedLikelihoodIfNoCopying + SumAdjustedLikeCopy)
  PosteriorNoCopying <- AdjustedLikelihoodIfNoCopying / (AdjustedLikelihoodIfNoCopying + SumAdjustedLikeCopy)
  
  if(Response == "Someone copied."){
    return(PosteriorCopying)
  } else {
    return(PosteriorNoCopying)
  }
}

```

## Full model- takes into account constraints of the puzzle box, as well as number of available choices to build with
```{r full model}

ModelFull = function(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate){
 
  # Take into account the physical constraints of the box: For StarBox, there's only 1 rod option that works. (All handle options always work, on both boxes. For circle box, all rod options work.)
  if(Box == 'Star'){
    NumRodChoices <- 1
  }
  
  ModelBase(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate)
}
```

##Ignores star constraint (ISC) model- does not take into account constraints of the puzzle box

```{r ignore star constraint model}
ModelISC = function(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate){

    # Note that in contrast to the full model, this model does not adjust the value of NumRodChoices to take into account the StarBox constraint.
  
    ModelBase(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate)

}
```

## Ignores NumChoices model: Ignores the number of options available (in terms of rod and handle piece choices)

```{r ignores numChoices model}
ModelIgnoresNumChoices = function(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate, nChoices){
 
  # Instead of taking into account the actual number of options, use a value that does not change/ is not sensitive to actual number of options (nChoice)
  NumHandleChoices <- nChoices
  if(Box == 'Cir'){
    NumRodChoices <- nChoices
  } else {
    NumRodChoices <- 1
  }
  
  ModelBase(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate)

}
```

```{r ignores star constraint and numChoices model}
ModelISCNumChoices = function(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate, nChoices){
 
  # Instead of taking into account the actual number of options, use a value that does not change/ is not sensitive to actual number of options (nChoice)
    NumRodChoices <- nChoices
    NumHandleChoices <- nChoices
  
  
  ModelBase(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate)

}
```

## Run the models to get posteriors
```{r all models}

posteriorFullModel <- ModelFull(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate)
posteriorFullModel

posteriorISCModel <- ModelISC(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate)
posteriorISCModel

posteriorIgnoresNumChoicesModel <- ModelIgnoresNumChoices(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate, nChoices)
posteriorIgnoresNumChoicesModel

posteriorISCNumChoicesModel <- ModelISCNumChoices(Box, HandleIsDiff, RodIsDiff, NumHandleChoices, NumRodChoices, priorCopy, Response, errorRate, nChoices)
posteriorIgnoresNumChoicesModel

```




