---
title: "IntArch_ClayTools_Adult_Model"
author: "Ethan Hurwitz"
date: "9/26/2018"
output: html_document
---

```{r setup, include=FALSE, message=FALSE}
library(tidyverse)
library(stats4)
library(papaja)
library(ggpmisc)
library(ggpubr)
library(pbapply)
```

#Data cleaning

```{r data cleaning}

dat <- read.csv("/Users/ethan/Downloads/IntArch_TestData.csv", stringsAsFactors = F)

#Filter out data to be excluded:

# #Memory check questions:
# ##Star box
# 
# dat %>%
#   filter(MemCheck_RodStar == "Star rod") %>% 
#   filter(MemCheck_RodCir == "All of the rod pieces") %>%
#   filter(MemCheck_HanCir == "All of the handle pieces") %>%
#   filter(MemCheck_HanStar == "All of the handle pieces")
# 
# #Score the lextale
# dat %>% 
#   mutate(score = (((apply(dat %>%
#   select(ends_with(match = "_Y")), 1, function(x) sum(x=="Yes, this is English")))/20*100) + ((apply(dat %>%
#   select(ends_with(match = "_N")), 1, function(x) sum(x=="No, this is not English")))/10*100))/2) 
# 
# ##Completion time
# dat$`timing_Page,Submit` <- as.numeric(as.character(dat$`timing_Page,Submit`))
# 
# mean(as.numeric(as.character(dat$`timing_Page,Submit`)))
# sd(as.numeric(as.character(dat$`timing_Page,Submit`)))*2
# 
# dat %>%
#   filter(`timing_Page,Submit` <= (mean(dat$`timing_Page,Submit`) + sd(dat$`timing_Page,Submit`)))


dat <- dat[-(1:2),-(1:18)]

names(dat) <- gsub("HId", "Iden", names(dat))

names(dat) <- gsub("RId", "Iden", names(dat))

names(dat) <- gsub("HDi", "Dif", names(dat))

names(dat) <- gsub("RDi", "Dif", names(dat))

names(dat) <- gsub("[.]", ",", names(dat))

dat.copy <- dat %>%
  select(-c(grep("Ha", names(dat)), grep("Ro", names(dat)), grep("Bo", names(dat)), ends_with(match = "H", vars = names(dat)), ends_with(match = "R", vars = names(dat)), ends_with(match = "B", vars = names(dat)))) %>%
  select(1:24)

dat.copy <- cbind(PID = 1:nrow(dat.copy), dat.copy)
```

##Tidy data

```{r tidy the data}
dat.copy2 = dat.copy %>%
  gather(condition, Result,-PID) %>%
  separate(condition, c('Box', 'HandleSimilarity', 'RodSimilarity', 'HandleChoices', 'RodChoices'),',') %>%
  mutate(HandleChoices = as.numeric(HandleChoices),
         RodChoices = as.numeric(RodChoices)) %>%
  filter(Result != "")
```


#Model creation

##full model

```{r full model}
model.full = function(Box, HandleSimilarity, RodSimilarity, HandleChoices, RodChoices, priorCopy, Response){
  
  if(Box == 'Star'){
    RodChoices <- 1
  }
  
  if(HandleSimilarity == 'Dif' & RodSimilarity == 'Dif'){
    likeCopy.all <- 0.00000000001
    likeCopy.HandleOnly <- 0.00000000001
    likeCopy.RodOnly <- 0.00000000001
    likelihoodIndep <- ((RodChoices-1)/RodChoices) * ((HandleChoices-1)/HandleChoices)
  } else if(HandleSimilarity == 'Dif' & RodSimilarity == 'Iden'){
    likeCopy.all <- 0.00000000001
    likeCopy.HandleOnly <- 0.00000000001
    likeCopy.RodOnly <- 1 * ((HandleChoices-1)/HandleChoices)
    likelihoodIndep <- (1/RodChoices) * ((HandleChoices-1)/HandleChoices)
  } else if(HandleSimilarity == 'Iden' & RodSimilarity == 'Dif'){
    likeCopy.all <- 0.00000000001
    likeCopy.HandleOnly <- ((RodChoices-1)/RodChoices) * 1
    likeCopy.RodOnly <- 0.000000000010
    likelihoodIndep <- ((RodChoices-1)/RodChoices) * (1/HandleChoices)
  } else if(HandleSimilarity == 'Iden' & RodSimilarity == 'Iden'){
    likeCopy.all <- 1
    likeCopy.HandleOnly <- (1/RodChoices) * 1
    likeCopy.RodOnly <- 1 * (1/HandleChoices)
    likelihoodIndep <- (1/RodChoices) * (1/HandleChoices)
  }
  adjusted.likeCopy.all <- priorCopy * priorCopy * likeCopy.all
  adjusted.likeCopy.HandleOnly <- (1 - priorCopy) * priorCopy * likeCopy.HandleOnly
  adjusted.likeCopy.RodOnly <- priorCopy * (1 - priorCopy) * likeCopy.RodOnly
  adjusted.likelihoodIndep <- (1 - priorCopy) * (1 - priorCopy) * likelihoodIndep
  
  sum.adjusted.likeCopy <- adjusted.likeCopy.all + adjusted.likeCopy.HandleOnly + adjusted.likeCopy.RodOnly
  
  posterior.copying <- sum.adjusted.likeCopy / (adjusted.likelihoodIndep + sum.adjusted.likeCopy)
  posterior.indep <- adjusted.likelihoodIndep / (adjusted.likelihoodIndep + sum.adjusted.likeCopy)
  
  
  if(Response == "Someone copied."){
    return(posterior.copying)
  } else {
    return(posterior.indep)
  }
}
```

##model that ignores star constraint (ISC):

```{r ignore star constraint model}
model.ISC = function(Box, HandleSimilarity, RodSimilarity, HandleChoices, RodChoices, priorCopy, Response){
  if(HandleSimilarity == 'Dif' & RodSimilarity == 'Dif'){
    likeCopy.all <- 0.00000000001
    likeCopy.HandleOnly <- 0.00000000001
    likeCopy.RodOnly <- 0.00000000001
    likelihoodIndep <- ((RodChoices-1)/RodChoices) * ((HandleChoices-1)/HandleChoices)
  } else if(HandleSimilarity == 'Dif' & RodSimilarity == 'Iden'){
    likeCopy.all <- 0.00000000001
    likeCopy.HandleOnly <- 0.00000000001
    likeCopy.RodOnly <- 1 * ((HandleChoices-1)/HandleChoices)
    likelihoodIndep <- (1/RodChoices) * ((HandleChoices-1)/HandleChoices)
  } else if(HandleSimilarity == 'Iden' & RodSimilarity == 'Dif'){
    likeCopy.all <- 0.00000000001
    likeCopy.HandleOnly <- ((RodChoices-1)/RodChoices) * 1
    likeCopy.RodOnly <- 0.00000000001
    likelihoodIndep <- ((RodChoices-1)/RodChoices) * (1/HandleChoices)
  } else if(HandleSimilarity == 'Iden' & RodSimilarity == 'Iden'){
    likeCopy.all <- 1
    likeCopy.HandleOnly <- (1/RodChoices) * 1
    likeCopy.RodOnly <- 1 * (1/HandleChoices)
    likelihoodIndep <- (1/RodChoices) * (1/HandleChoices)
  }
  adjusted.likeCopy.all <- priorCopy * priorCopy * likeCopy.all
  adjusted.likeCopy.HandleOnly <- (1 - priorCopy) * priorCopy * likeCopy.HandleOnly
  adjusted.likeCopy.RodOnly <- priorCopy * (1 - priorCopy) * likeCopy.RodOnly
  adjusted.likelihoodIndep <- (1 - priorCopy) * (1 - priorCopy) * likelihoodIndep
  
  sum.adjusted.likeCopy <- adjusted.likeCopy.all + adjusted.likeCopy.HandleOnly + adjusted.likeCopy.RodOnly
  
  posterior.copying <- sum.adjusted.likeCopy / (adjusted.likelihoodIndep + sum.adjusted.likeCopy)
  posterior.indep <- adjusted.likelihoodIndep / (adjusted.likelihoodIndep + sum.adjusted.likeCopy)
  
  
  if(Response == "Someone copied."){
    return(posterior.copying)
  } else {
    return(posterior.indep)
  }
}
```

#Full model

##likelihood function for mle()

```{r Full model likelihood Function Wrapper}
copy.llh.full = function(priorCopy){
  tempData = dat.copy2 %>%
    rowwise() %>%
    mutate(pred = model.full(Box, HandleSimilarity, RodSimilarity, HandleChoices, RodChoices, priorCopy, Result))
  -sum(log(tempData$pred))
}
```

##Run mle() to find best prior and the likelihood

```{r Full model mle}
#cannot use 0 and 1 because it will result in (NaN)
lwrs.full = c(0.000000001)
uprs.full = c(0.999999999)
inits.full = list(priorCopy = mean(dat.copy2$Result == "Someone copied."))

fit.full <- mle(copy.llh.full, start = inits.full, lower = lwrs.full, upper = uprs.full, method = 'L-BFGS-B')

summary(fit.full) #-2logLik for all data

#coef(fit.full) to pull out the coefficients (prior/parameters)
#logLik(fit.full) to pull out the -loglik
```

##bootstrap subjects to get errorbars on BICs

###Function to create new samples

```{r bootstrap sample function}
x.new = function(){sample_n(dat.copy, nrow(dat.copy), replace=TRUE) %>% 
    gather(condition, Result, -PID) %>%
    separate(condition, c('Box', 'HandleSimilarity', 'RodSimilarity', 'HandleChoices', 'RodChoices'),',') %>%
    mutate(HandleChoices = as.numeric(HandleChoices),
           RodChoices = as.numeric(RodChoices)) %>%
    filter(Result != "")
    } 
```

###function to create new BICs from random sample

```{r new full model BICs from samples}
#Because all of the below are using randomly generated samples, they have to be contained within the same function(/environment) otherwise they will be using different samples.

ResampleBics.full = function(){temp = x.new()
test.llh.full = function(priorCopy){
  tempData = temp %>%
    rowwise() %>%
    mutate(pred = model.full(Box, HandleSimilarity, RodSimilarity, HandleChoices, RodChoices, priorCopy, Result))
  -sum(log(tempData$pred))
}
inits.test.full = list(priorCopy = mean((temp %>% 
                                      select(Result)) == "Someone copied."))
fit.test.full <- mle(test.llh.full, start = inits.test.full, lower = lwrs.full, upper = uprs.full, method = 'L-BFGS-B')
return(((-2*logLik(fit.test.full)[1])+(1*nrow(temp))))
}
```

###bootstrap BICs for full model

```{r bootstrap BICs for full model}
samples.full <- pbreplicate(10000,ResampleBics.full())
mean(samples.full)
quantile(samples.full, c(0.025, 0.975))
full.df <- data.frame(Model = 'Full.Model',
                      bic.mean = mean(samples.full),
                      bic.upper = mean(samples.full) + sd(samples.full),
                      bic.lower = mean(samples.full) - sd(samples.full))
```


#Model that ignores the starbox constraint (ISC)

##ISC model likelihood function for mle()

```{r ISC model likelihood function wrapper}
copy.llh.ISC = function(priorCopy){
  tempData = dat.copy2 %>%
    rowwise() %>%
    mutate(pred = model.ISC(Box, HandleSimilarity, RodSimilarity, HandleChoices, RodChoices, priorCopy, Result))
  -sum(log(tempData$pred))
}
```

##Run mle() to find best prior and the likelihood

```{r ISC model mle}
#since only the model and likelihood function wrapper change here, can use the upper, lower, and starting values above.
fit.ISC <- mle(copy.llh.ISC, start = inits.full, lower = lwrs.full, upper = uprs.full, method = 'L-BFGS-B')

summary(fit.ISC)
```

##bootstrap subjects to get errorbars on BICs

###function to create new BICs from random sample

```{r new ISC model BICs from samples}
ResampleBics.ISC = function(){temp = x.new()
test.llh.ISC = function(priorCopy){
  tempData = temp %>%
    rowwise() %>%
    mutate(pred = model.ISC(Box, HandleSimilarity, RodSimilarity, HandleChoices, RodChoices, priorCopy, Result))
  -sum(log(tempData$pred))
}
inits.test.ISC = list(priorCopy = mean((temp %>% 
                                      select(Result)) == "Someone copied."))
fit.test.ISC <- mle(test.llh.ISC, start = inits.test.ISC, lower = lwrs.full, upper = uprs.full, method = 'L-BFGS-B')
return(((-2*logLik(fit.test.ISC)[1])+(1*nrow(temp))))
}
```

###bootstrap BICs for ISC model

```{r bootstrap BICs for ISC model}
samples.ISC <- pbreplicate(10000,ResampleBics.ISC())
mean(samples.ISC)
quantile(samples.ISC, c(0.025, 0.975))

ISC.df <- data.frame(Model = 'ISC.Model',
                      bic.mean = mean(samples.ISC),
                      bic.upper = mean(samples.ISC) + sd(samples.ISC),
                      bic.lower = mean(samples.ISC) - sd(samples.ISC))
```

#Model that ignores the number of options, e.g., 1/10 becomes 1/N. (nChoice):

##likelihood function for mle()

```{r nChoice likelihood function wrapper}
copy.llh.nChoice = function(priorCopy, nChoices){
  tempData = dat.copy2 %>%
    rowwise() %>%
    mutate(pred = model.full(Box, HandleSimilarity, RodSimilarity, nChoices, nChoices, priorCopy, Result))
  -sum(log(tempData$pred))
}
```

##Run mle() to find best prior, best number of options, and the likelihood

```{r nChoice model mle}
lwrs.nChoice = c(0.000000001, 1.000000001) #different values for nchoices
uprs.nChoice = c(0.999999999, Inf)
inits.nChoice = list(priorCopy = mean(dat.copy2$Result == "Someone copied."),
             nChoices = round(mean(c(dat.copy2$HandleChoices, dat.copy2$RodChoices))))

fit.nChoice = mle(copy.llh.nChoice, start = inits.nChoice, lower = lwrs.nChoice, upper = uprs.nChoice, method = 'L-BFGS-B')

summary(fit.nChoice)
```

##bootstrap subjects to get errorbars on BICs

###function to create new BICs from random sample

```{r new nChoice model BICs from samples}
ResampleBics.nChoice = function(){temp = x.new()
test.llh.nChoice = function(priorCopy, nChoices){
  tempData = temp %>%
    rowwise() %>%
    mutate(pred = model.full(Box, HandleSimilarity, RodSimilarity, nChoices, nChoices, priorCopy, Result))
  -sum(log(tempData$pred))
}
inits.test.nChoice = list(priorCopy = mean((temp %>% 
                                              select(Result)) == "Someone copied."),
                          nChoices = round(mean(c(temp$HandleChoices, temp$RodChoices))))
fit.test.nChoice <- mle(test.llh.nChoice, start = inits.test.nChoice, lower = lwrs.nChoice, upper = uprs.nChoice, method = 'L-BFGS-B')
return(((-2*logLik(fit.test.nChoice)[1])+(2*nrow(temp))))
}
```

###bootstrap BICs for nChoice model

```{r bootstrap BICs for nChoice model}
samples.nChoice <- pbreplicate(10000,ResampleBics.nChoice())
mean(samples.nChoice)
quantile(samples.nChoice, c(0.025, 0.975))

nChoice.df <- data.frame(Model = 'nChoice.Model',
                      bic.mean = mean(samples.nChoice),
                      bic.upper = mean(samples.nChoice) + sd(samples.nChoice),
                      bic.lower = mean(samples.nChoice) - sd(samples.nChoice))
```

#Build model that ignores the star constraint AND the number of options (ISCnChoice):

##likelihood function for mle()

```{r ISCnChoice model likelihood function wrapper}
copy.llh.ISCnChoice = function(priorCopy, nChoices){
  tempData = dat.copy2 %>%
    rowwise() %>%
    mutate(pred = model.ISC(Box, HandleSimilarity, RodSimilarity, nChoices, nChoices, priorCopy, Result))
  -sum(log(tempData$pred))
}
```

##Run mle() to find best prior, best number of choices, and the likelihood

```{r ISCnChoice model mle}
#Again, all that's changed is the model, so we can just use the start, lower, and upper, values from above

fit.ISCnChoice = mle(copy.llh.ISCnChoice, start = inits.nChoice, lower = lwrs.nChoice, upper = uprs.nChoice,
           method = 'L-BFGS-B')

summary(fit.ISCnChoice)
```

##bootstrap subjects to get errorbars on BICs

###function to create new BICs from random sample

```{r new ISCnChoice model BICs from samples}
ResampleBics.ISCnChoice = function(){temp = x.new()
test.llh.ISCnChoice = function(priorCopy, nChoices){
  tempData = temp %>%
    rowwise() %>%
    mutate(pred = model.ISC(Box, HandleSimilarity, RodSimilarity, nChoices, nChoices, priorCopy, Result))
  -sum(log(tempData$pred))
}
inits.test.ISCnChoice = list(priorCopy = mean((temp %>% 
                                              select(Result)) == "Someone copied."),
                          nChoices = round(mean(c(temp$HandleChoices, temp$RodChoices))))
fit.test.ISCnChoice <- mle(test.llh.ISCnChoice, start = inits.test.ISCnChoice, lower = lwrs.nChoice, upper = uprs.nChoice, method = 'L-BFGS-B')
return(((-2*logLik(fit.test.ISCnChoice)[1])+(2*nrow(temp))))
}
```

###bootstrap BICs for ISCnChoice model

```{r bootstrap BICs for ISCnChoice model}
samples.ISCnChoice <- pbreplicate(10000,ResampleBics.ISCnChoice())
mean(samples.ISCnChoice)
quantile(samples.ISCnChoice, c(0.025, 0.975))

ISCnChoice.df <- data.frame(Model = 'ISCnChoice.Model',
                      bic.mean = mean(samples.ISCnChoice),
                      bic.upper = mean(samples.ISCnChoice) + sd(samples.ISCnChoice),
                      bic.lower = mean(samples.ISCnChoice) - sd(samples.ISCnChoice))
```

#Summarize MLE derived best parameters:

```{r summary table of best parameters}
data.frame("Model" = c("Full", "ISC", "nChoice", "ISCnChoice"), "Best Prior" = c(round(coef(fit.full), 2), round(coef(fit.ISC), 2), round(coef(fit.nChoice)[1], 2), round(coef(fit.ISCnChoice)[1], 2)), "Best nChoice" = c(NA,NA,round(coef(fit.nChoice)[2], 2), round(coef(fit.ISCnChoice)[2], 2)))

dfs <- rbind(full.df, ISC.df, nChoice.df, ISCnChoice.df) #combine summary of resampled data
```

#compare BICs from the different models

```{r model BIC comparisons}
#Find BICs:
(-2*logLik(fit.full)[1])+(1*nrow(dat.copy2)) #full model BIC
(-2*logLik(fit.ISC)[1])+(1*nrow(dat.copy2)) #ISC model BIC
(-2*logLik(fit.nChoice)[1])+(2*nrow(dat.copy2)) #nChoice model BIC
(-2*logLik(fit.ISCnChoice)[1])+(2*nrow(dat.copy2)) #ISC and nChoice model BIC

#Graph BICs:
data.frame("Full Model" = (-2*logLik(fit.full)[1])+(1*nrow(dat.copy2)), "ISC Model" = (-2*logLik(fit.ISC)[1])+(1*nrow(dat.copy2)), "nChoice Model" = (-2*logLik(fit.nChoice)[1])+(2*nrow(dat.copy2)), "ISCnChoice Model" = (-2*logLik(fit.ISCnChoice)[1])+(2*nrow(dat.copy2))) %>%
  gather(Model, BIC) %>%
  ggplot(aes(x = Model, y = BIC, fill = Model)) +
  geom_bar(stat = "identity") +
  geom_errorbar(data = dfs, aes(x=Model, y = bic.mean, ymin = bic.lower,ymax = bic.upper), width = .33)+
  scale_x_discrete(limits=c("Full.Model","ISC.Model","nChoice.Model", "ISCnChoice.Model")) +
  theme_apa() + 
  guides(fill=FALSE) +
  xlab("Model") +
  ylab("BIC")+
  theme(axis.text.x = element_text(angle = 45, hjust=1))

```



